Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-20 paper.tex
Tweak designing benchmarks => designing meaningful benchmarks

\section{Building Benchmarks} \label{sec:bench}
Experience with applications deployed on Cog shows that memory intensive applications often exhibit three distinct regimes.  As an application builds a new data structure the heap grows, and the garbage collector should be biassed to allow growth, rather than to favour performing garbage collection when the current size of the heap is reached.  As an application processes the data structure it has built the heap is stable, at least in its size.  If the application then releases significant storage and continues processing, the garbage collector should favour reclamation, and it is advantageous if it attempts to free up memory segments and return them to the OS.  We have identified, therefore, growing, stable and shrinking regimes, and these are useful abstractions of real application behaviour, which are helpful in designing benchmarks and in providing tuning mechanisms to the system programmer.

>>>>

\section{Building Benchmarks} \label{sec:bench}
Experience with applications deployed on Cog shows that memory intensive applications often exhibit three distinct regimes.  As an application builds a new data structure the heap grows, and the garbage collector should be biassed to allow growth, rather than to favour performing garbage collection when the current size of the heap is reached.  As an application processes the data structure it has built the heap is stable, at least in its size.  If the application then releases significant storage and continues processing, the garbage collector should favour reclamation, and it is advantageous if it attempts to free up memory segments and return them to the OS.  We have identified, therefore, growing, stable and shrinking regimes, and these are useful abstractions of real application behaviour, which are helpful in designing meaningful benchmarks and in providing tuning mechanisms to the system programmer.
